Modalities for Virtualizing Memory Addresses

### 2022-12-04 intro.tex
+

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor.
%Despite its modal flavor, up until now, program logic have taken the contingency to be asserted as a qualified-predicate, e.g. \textit{Stackable} ~\cite{}, and built a mechanism, a decorated weakest-precondition, to operated on these certain type predicates. On the other, we, in this paper, propose
%\begin{itemize}
%\item {more light-weight} such that
%  \begin{itemize}
%  \item modal abstractions remove the burden of carrying the resource that ---
%  \item >>>contingency as a modal abstractions
%  \item 
%  \item we do no
%  \end{itemize}
%\item {more intuitive} modal abstraction definition, together with relations defined
%\begin{itemized}
%  \end{itemize}
%\end{itemize}
We propose tackling the verification of virtual memory subsystems (and kernels more broadly) by adapting ideas from hybrid modal logic, which can label assertions true under \emph{other} circumstances (i.e., in another address space) with a modality indexed by a name for that space (in our case, the root of the page tables for an address space). This offers a convenient and powerful way to modularly (1) isolate assertions specific to a particular address space, (2) explicitly state when an assertion is true across address spaces, (3) manipulate address spaces from within other address spaces, and (4) reason about change in address spaces. These advantages make this approach to reasoning about virtual memory more flexible than prior program logic techniques~\cite{kolanski08vstte,kolanski09tphols}, which was only able to work with a single address space (the current address space on the CPU).

>>>>

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor%., and manifets itself at many other verification challenges besides the one, virtual-memory-management, we take as a challenge in this paper. For example, Monie et.al. ~\cite{}, introduces a theory for heap management under the existence of garbage collection where  which relies on two pillars: 1. a predicate 
%Despite its modal flavor, up until now, program logic have taken the contingency to be asserted as a qualified-predicate, e.g. \textit{Stackable} ~\cite{}, and built a mechanism, a decorated weakest-precondition, to operated on these certain type predicates. On the other, we, in this paper, propose
%\begin{itemize}
%\item {more light-weight} such that
%  \begin{itemize}
%  \item modal abstractions remove the burden of carrying the resource that ---
%  \item >>>contingency as a modal abstractions
%  \item 
%  \item we do no
%  \end{itemize}
%\item {more intuitive} modal abstraction definition, together with relations defined
%\begin{itemized}
%  \end{itemize}
%\end{itemize}
We propose tackling the verification of virtual memory subsystems (and kernels more broadly) by adapting ideas from hybrid modal logic, which can label assertions true under \emph{other} circumstances (i.e., in another address space) with a modality indexed by a name for that space (in our case, the root of the page tables for an address space). This offers a convenient and powerful way to modularly (1) isolate assertions specific to a particular address space, (2) explicitly state when an assertion is true across address spaces, (3) manipulate address spaces from within other address spaces, and (4) reason about change in address spaces. These advantages make this approach to reasoning about virtual memory more flexible than prior program logic techniques~\cite{kolanski08vstte,kolanski09tphols}, which was only able to work with a single address space (the current address space on the CPU).
